Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-14 VMCAI-revised-version/final.tex
section

Let us prove $2 \implies 1$. Let $s_1, t_1 , s_2 \in S$ with $s_2 \leq s_1$  and $s_1 \rightarrow t_1$, Consider $\pred^*(\downarrow t_1)$; since $s_1 \rightarrow t_1$ we deduce that $s_1 \in \pred^*(\downarrow t_1)$, and since $s_2 \leq s_1$ and $\pred^*(\downarrow t_1)$ is downward-closed, we also have $s_2 \in \pred^*(\downarrow t_1)$. This means that there exists $t_2 \leq t_1$ such that 
$s_2 \rightarrow^{*} t_2$. Hence, we proved that $\mathscr{S}$ is downward compatible.
\qed

>>>>

Let us prove $2 \implies 1$. Let $s_1, t_1 , s_2 \in S$ with $s_2 \leq s_1$  and $s_1 \rightarrow t_1$, Since $s_1 \rightarrow t_1$ we deduce that $s_1 \in \pred^*(\downarrow t_1)$, and since $s_2 \leq s_1$ and $\pred^*(\downarrow t_1)$ is downward-closed, we also have $s_2 \in \pred^*(\downarrow t_1)$. This means that there exists $t_2 \leq t_1$ such that 
$s_2 \rightarrow^{*} t_2$. Hence, we proved that $\mathscr{S}$ is downward compatible.
\qed
